An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-17 indicators/paper/paper.tex
Discussion copyedits

Third, the underlying database tracks all revisions made to the data, allowing
us to query the API to learn ``what was known when'', critical for understanding
the behavior (and potential pitfalls) of real-time surveillance signals. Such
revision data is rarely available in standardized format from other sources.

>>>>

Third, the underlying database tracks all revisions made to the data, allowing
us to query the API to learn ``what was known when'', which is critical for
understanding the behavior (and potential pitfalls) of real-time surveillance
signals. Such revision data is rarely available in standardized format from
other sources.
